Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-12 paper/paper.tex
adding hermes bug in discussion

\vspace{1ex}\noindent\textbf{Issue \#35, Table~\ref{tab:bugs}.} We
reported the snippet \CodeIn{"use strict" 010} to the
\textbf{\smonkey} development team as a bug and the bug was confirmed
in a few hours.  This is a test case original from the \hermes suite
using test transplantation.  According the specification, in strict
mode, the engine must use the prefix '0o' or '0O' to represents octal
numeric literals. It was an issue which explores a deprecated octal
token after ASI (Automatic Semicolon Insertion).  The others engine
throws a SyntaxError due the missing of the octal token, but \smonkey
returns a integer 8 that represents 010 in octal.

@@

>>>>

\vspace{1ex}\noindent\textbf{Issue \#35, Table~\ref{tab:test-transplantation-bugs}.} We
reported the snippet \CodeIn{"use strict" 010} to the
\textbf{\smonkey} development team as a bug and the bug was confirmed
in a few hours.  This is a test case original from the \hermes suite
using test transplantation.  According the specification, in strict
mode, the engine must use the prefix '0o' or '0O' to represents octal
numeric literals. It was an issue which explores a deprecated octal
token after ASI (Automatic Semicolon Insertion).  The others engine
throws a SyntaxError due the missing of the octal token, but \smonkey
returns a integer 8 that represents 010 in octal.

@@

\vspace{1ex}\noindent\textbf{Issue \#24, Table~\ref{tab:bugs}.} The snippet 
\CodeIn{b+/v/a} represents a bug confirmed in \hermes\ engine with 
differential testing using radamsa on a repository mined from GitHub.
The original test case contains a string concatenation. 
This is a case of validation of RegExp flags. The fuzzer mutate
the file with a regular expression "/v/" between the plus operator and
the variable. The plus operator in this case is used as a flag of the RegExp "+/v/",
but in this case the plus operator is not valid. The behavior expected
is throws an early SyntaxError due to a invalid regular expression flag,
but \hermes Hermes seems not treats the early validation of the regexp flags
as commented by a maintainer.
